### 2024-01-26 docs/results/arima.qmd
Explore monthly seasonality

reportMod <- function(mods) {
  require("kableExtra")
  tar_load(med_groups)
  spec  <- lapply(mods, forecast::arimaorder) %>% sapply(paste, collapse = ", ")
  label <- sprintf("%s (%s)", med_groups, spec)
  res   <- mods %>%
    set_names(label) %>%
    lapply(function(mod) {
      mod %>% lmtest::coeftest() %>% broom::tidy() %>% data.frame()
    }) %>%
    {do.call(rbind, .)} %>%
    tibble::add_column("Model" = gsub(x = rownames(.), "\\..*", ""), .before = 1) %>%
    set_rownames(c()) %>%
    kable(longtable = TRUE, booktabs = TRUE) %>%
    kable_styling(font_size = 10, latex_options = c("repeat_header"))

>>>>

reportMod <- function(mods) {
  require("kableExtra")
  tar_load(med_groups)
  spec  <- lapply(mods, forecast::arimaorder) %>% sapply(paste, collapse = ", ")
  label <- sprintf("%s (%s)", med_groups, spec)
  res   <- mods %>%
    set_names(label) %>%
    lapply(function(mod) {
      tryCatch(
        mod %>% lmtest::coeftest() %>% broom::tidy() %>% data.frame(),
        error = function(e) { # In case error due to no AR nor MA component
          data.frame(
            "term" = NA,
            "estimate" = NA,
            "std.error" = NA,
            "statistic" = NA,
            "p.value" = NA
          )
        }
      )
    }) %>%
    subset(subset = !is.na(.)) %>%
    {do.call(rbind, .)} %>%
    tibble::add_column("Model" = gsub(x = rownames(.), "\\..*", ""), .before = 1) %>%
    set_rownames(c()) %>%
    kable(longtable = TRUE, booktabs = TRUE) %>%
    kable_styling(font_size = 10, latex_options = c("repeat_header"))
